Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-22 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
explain which matrices are scaled
added sentence about RIP not even holding for scaled matrices

We use a testset consisting of 63 matrices of the following seven
different types: band matrices,
with band size three or five with entries within the band chosen uniformly in $\{0,1\}$, binary matrices with all entries chosen 
uniformly in $\{0,1\}$, Gaussian-distributed matrices, and rank one 
matrices $A = aa\T$ with $N(0,1)$-distributed entries of $a$. In addition to these four types,
we also use three more with theoretical results on their restricted isometry
constants. These include matrices with 
$N(0, 1/m)$-distributed entries, with entries chosen uniformly in $\pm 1/\sqrt{m}$, and finally with distribution
\begin{equation}\nonumber
  A_{ij} = \begin{cases}
    + \sqrt{3/m} & \text{with probability } \frac{1}{6}, \\
    0 & \text{with probability } \frac{2}{3}, \\
    - \sqrt{3/m} & \text{with probability } \frac{1}{6}.
  \end{cases}
\end{equation}
For each type we used \mbox{MATLAB 8.3.0} to randomly generate nine
matrices of three different sizes with the number of rows ranging from 15
to 30, number of columns
from 25 to 40, and order $k$ between three and five, see Table~\ref{matrixsizes}.

@@

\color{red}The restricted isometry constants of all matrices can be found in the appendix. Note that for the unscaled matrices,
the restricted isometry constants can be expected to be much larger than for the scaled ones. Furthermore, since we solved
the instances with a feasibility tolerance of $10^{-6}$, which influences the optimal objective by a factor of the
largest objective coefficients and the number of variables, the computed constants are only exact up to a factor
of about $10^{-2}$ for these matrices, while the precision is much better for the normalized ones because of their
smaller objective coefficients.\color{black}

>>>>

We use a testset consisting of 63 matrices of the following seven
different types: band matrices,
with band size three or five with entries within the band chosen uniformly in $\{0,1\}$, binary matrices with all entries chosen 
uniformly in $\{0,1\}$, Gaussian-distributed matrices, and rank one 
matrices $A = aa\T$ with $N(0,1)$-distributed entries of $a$. In addition to these four types,
we also use three types of scaled matrices with theoretical results on their restricted isometry
constants. These include matrices with 
$N(0, 1/m)$-distributed entries, with entries chosen uniformly in $\pm 1/\sqrt{m}$, and finally with distribution
\begin{equation}\nonumber
  A_{ij} = \begin{cases}
    + \sqrt{3/m} & \text{with probability } \frac{1}{6}, \\
    0 & \text{with probability } \frac{2}{3}, \\
    - \sqrt{3/m} & \text{with probability } \frac{1}{6}.
  \end{cases}
\end{equation}
For each type we used \mbox{MATLAB 8.3.0} to randomly generate nine
matrices of three different sizes with the number of rows ranging from 15
to 30, number of columns
from 25 to 40, and order $k$ between three and five, see Table~\ref{matrixsizes}.

@@

The restricted isometry constants of all matrices can be found in the appendix. Note that for the unscaled matrices,
the restricted isometry constants can be expected to be much larger than for the scaled ones. Even for the scaled
matrices, the restricted isometry property did not hold for any of the matrices in the testset, since the instances
were too small to satisfy the needed relation between $n$ and $k$.
\color{red} Furthermore, since we solved
the instances with a feasibility tolerance of $10^{-6}$, which influences the optimal objective by a factor of the
largest objective coefficients and the number of variables, the computed constants are only exact up to a factor
of about $10^{-2}$ for the unscaled matrices, while the precision is much better for the normalized ones because of their
smaller objective coefficients.\color{black}
